%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.
    % The font could be set to Windows-specific Calibri by using the 'calibri' option
    \documentclass[]{mcdowellcv}

    % For mathematical symbols
	\usepackage{amsmath}
	\usepackage{url}
	\usepackage{hyperref}

    
      % Set applicant's personal data for header
      \name{Jacob Rodal}
      \address{\href{https://www.jrodal.dev}{jrodal.dev} \linebreak \href{https://www.github.com/jrodal98}{github.com/jrodal98}}
      \contacts{jr6ff@virginia.edu \linebreak 703-283-9318}
    

    \begin{document}
% Print the header
\makeheader
      

\begin{cvsection}{Education}
	\begin{cvsubsection}{BS in Computer Science}{University of Virginia}{Graduating in Dec 2020}
		\begin{itemize}
			\item BS in Computer Science, BA in Statistics. \textbf{Cumulative GPA: 3.94}
			\item Selected Coursework: Algorithms, Machine Learning, Data Structures, Cybersecurity, Software Engineering Methods, Applied Linear Models, Linear Algebra, Probability, Mathematical Statistics 
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}
\begin{cvsection}{Experience}
    \begin{cvsubsection}{Research Assistant}{University of Virginia}{Sept 2019 -- Current}
		\begin{itemize}%
			\item Investigating the use of MANETs (Mobile Ad Hoc Networks) to enable a connected transport system between autonomous vehicles.
			\item Currently developing an Android mobile application with Kotlin to test the feasibility of ad-hoc communication between pedestrians and autonomous vehicles.
		\end{itemize}
	\end{cvsubsection}

	\begin{cvsubsection}{Software Engineer Intern}{Leidos}{May 2019 -- Sept 2019}
		\begin{itemize}%
			\item Contributed to the development of open source simultaneous localization and mapping (SLAM) libraries in order to reconstruct 3-D point cloud models from real time video streams.
			\begin{itemize}
				\item Added support to allow multiple video streams to contribute towards a single reconstruction.
				\item Created bag of visual words vocabulary training pipeline for binary descriptors.
			\end{itemize}
			
			\item Led the development of a rust web server capable of directing incoming video data into SLAM processes and directing SLAM data to connected clients.
			\item Gained experience with computer vision, machine learning, rust, C++, python, docker, git, and gdb.
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Teaching Asssistant}{University of Virginia}{Aug 2018 -- May 2019}
		            
		\begin{itemize}%
			\item Provided assistance on problem sets during lectures to 150 ordinary differential equation students.  Graded exams, quizzes, and daily homework assignments.
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}
\begin{cvsection}{Personal Projects (Source Code Available on Github)}
	\begin{cvsubsection}{}{}{}
		\begin{itemize}
			\setlength\itemsep{3pt}
			\item \textbf{Grade Manager}  Fully featured PyQT5 desktop application for tracking grades across multiple courses. Supports various grading schemes and offers one light and two dark themes.
			\item \textbf{PDF-Packages}  TkInter desktop application for bookmarking, combining, and converting PDFs.
			\item \textbf{Paginated Table Extractor}  Highly efficient data extractor designed to completely automate the extraction of data from HTML tables that only show a subset of all available data per page. 
			\item \textbf{Whoopie Pie Bot}  A python bot that emails subscribers whenever the University of Virginia dining menus mention whoopie pies.  Deployed on a raspberry pi zero. 
			\item \textbf{Dotfiles}  My arch linux, i3, polybar, xresources, zsh, st terminal, nvim, and various other configuration files are available to download so that my desktop environment can be easily emulated by others.
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}
\begin{cvsection}{Technical Skills}
	\begin{cvsubsection}{}{}{}
		\begin{itemize}
			\item \textbf{Programming Languages}:  Python, C++, Java, Rust, R, Kotlin, HTML, CSS, SQL
			\item \textbf{Linux}: Debian, RPM, and Arch based distributions. Shell scripting with bash, zsh, and python.
			\item \textbf{Others}:  Git, Docker, Django, QT, Tkinter, Opencv, Numpy, Pandas, Tensorflow, GDB
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}

\end{document}
